Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Some more conclusions and perspective

We designed out study to answer these two questions in a controlled experiment that mimics a real data analysis session.
RQ2 of course only makes sense if the answer to RQ1 is yes but we have reason to believe it is.

@@

In this study, we found that exposure to approximate data prior to seeing the precise data biases the observations people make.
This has important implications for the design of applications that present approximate results as well as for journalists who report for example polls before votes.
In this paper we tried to reduce the bias by making people aware of the approximate result they have previously seen but we did not see a significant reduction of the bias.
In future work, we should focus of usable methods to reduce the bias that can be used by approximate visualization tools and journalists.

>>>>

We designed our study to answer these two questions in a controlled experiment that mimics a real data analysis session.
RQ2 of course only makes sense if the answer to RQ1 is yes but we have reason to believe it is.

@@

The questions we try to answer in this paper in a more general sense are what negative effects seeing a less precise model before a more precise one has on how well people recollect the more precise data.
We focused on the specific case where a user only sees one approximate model before the precise one but the findings should generalize to the progressive case because there is nothing inherently different about the precise model.
The problem of seeing imprecise models before precise ones is relevant in a number of domains from journalists who may show poll results before the votes, a machine learning expert who builds models, to an economist who presents the forecast of economical development.
In this paper, we focused on data exploration in approximate query processing systems with the goal of finding actionable insights that inform how we design such systems.

In this study, we found that exposure to approximate data prior to seeing the precise data biases the observations people make.
This has important implications for the design of applications that present approximate results as well as for journalists who report for example polls before votes.
In this paper we tried to reduce the bias by making people aware of the approximate result they have previously seen but we did not see a significant reduction of the bias.

In future work, we should focus of usable methods to reduce the bias that can be used by approximate visualization tools.
Future work should also investigate how the findings from this paper generalize to other applications.
